%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EPFL report package, main thesis file
% Goal: provide formatting for theses and project reports
% Author: Mathias Payer <mathias.payer@epfl.ch>
%
% To avoid any implication, this template is released into the
% public domain / CC0, whatever is most convenient for the author
% using this template.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,11pt,oneside]{report}
% Options: MScThesis, BScThesis, MScProject, BScProject
\usepackage[MScThesis,lablogo]{EPFLreport}
\usepackage{xspace}

% added packages
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{float}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{xltabular}

\title{Tritium extraction and transport from molten salt breeding experiments}
\author{Hippolyte Monroe}
\supervisor{Dr. Rémi Delaporte-Mathurin}
\adviser{Dr. Mathieu Hursin}
%\coadviser{Second Adviser}
\expert{The External Reviewer}

% custom commands
\newcommand{\sysname}{FooSystem\xspace}
\newcommand{\PT}{\ensuremath{P_{T_2}}}
\newcommand{\CT}{\ensuremath{c_{T_2}}}
\newcommand{\JT}{\ensuremath{J_{T_2}}}
\newcommand{\YT}{\ensuremath{y_{T_2}}}

\begin{document}
\maketitle
\makededication
\makeacks

\begin{abstract}
The \sysname tool enables lateral decomposition of a multi-dimensional
flux compensator along the timing and space axes.

The abstract serves as an executive summary of your project.
Your abstract should cover at least the following topics, 1-2 sentences for
each: what area you are in, the problem you focus on, why existing work is
insufficient, what the high-level intuition of your work is, maybe a neat
design or implementation decision, and key results of your evaluation.
\end{abstract}

\begin{frenchabstract}
For a doctoral thesis, you have to provide a French translation of the
English abstract. For other projects this is optional.
\end{frenchabstract}

\maketoc

\input{notations}

%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
%%%%%%%%%%%%%%%%%%%%%%

The introduction is a longer writeup that gently eases the reader into your
thesis~\cite{dinesh20oakland}. Use the first paragraph to discuss the setting.
In the second paragraph you can introduce the main challenge that you see.
The third paragraph lists why related work is insufficient.
The fourth and fifth paragraphs discuss your approach and why it is needed.
The sixth paragraph will introduce your thesis statement. Think how you can
distill the essence of your thesis into a single sentence.
The seventh paragraph will highlight some of your results
The eights paragraph discusses your core contribution.

This section is usually 3-5 pages.

%%%%%%%%%%%%%%%%%%%%
\chapter{Background}
%%%%%%%%%%%%%%%%%%%%

The background section introduces the necessary background to understand your
work. This is not necessarily related work but technologies and dependencies
that must be resolved to understand your design and implementation.

This section is usually 3-5 pages.


%%%%%%%%%%%%%%%%
\chapter{Gas sparging model}
%%%%%%%%%%%%%%%%

% Introduce and discuss the design decisions that you made during this project.
% Highlight why individual decisions are important and/or necessary. Discuss
% how the design fits together.

% This section is usually 5-10 pages.

\section{Mathematical framework}
\subsection{Mass transfer}
% expose diffusivity, boundary layer model, then advective transport 
\subsection{Fluid dynamics}
% expose correlations

\subsection{Advection-reaction-dispersion model}
\begin{itemize}
    \item Liquid: 
    \begin{equation}
    \label{eq:CT2}
        \varepsilon_l \frac{\partial c_{T_2}}{\partial t} =  \underbrace{\varepsilon_l E_{l} \frac{\partial ^2 c_{T_{2}}}{\partial z^2}}_\text{liquid dispersion} + \underbrace{S_{T_2}}_\text{tritium source} - \underbrace{a\,J_{T_2}}_{\text{mass transfer}}
    \end{equation}
    \item Gas: 
    \begin{equation}
    \label{eq:PT2}
        \varepsilon_g \frac{1}{RT} \frac{\partial P_{T_2}}{\partial t} = \underbrace{-\frac{1}{RT}\frac{\partial (\,u_g\,P_{T_2})}{\partial z}}_\text{gas advection} + \underbrace{\varepsilon_g E_{g} \frac{1}{RT}\frac{\partial ^2 P_{T_{2}}}{\partial z^2}}_\text{gas dispersion} + a\,J_{T_2}
    \end{equation}
\end{itemize}
\subsection{Boundary conditions}
\subsection{Assumptions of the model}

\section{Numerical implementation}
% The implementation covers some of the implementation details of your project.
% This is not intended to be a low level description of every line of code that
% you wrote but covers the implementation aspects of the projects.

% This section is usually 3-5 pages.

\subsection{Python package structure}
% just a quick figure of the packages dependencies, API
\subsection{Numerical scheme}
\subsection{Fluid dynamics parameters resolution}
% parameters dependance graph
% graph resolution algorithm 

\subsection{Verification}
\subsubsection{Method of manufactured solution}
\subsubsection{Numerical error estimate}
% convergence plot: quantify convergence without tau at that point ? (not already introduced)
% add a MMS verification


\section{Model exploration}
% all that was learn by playing around with the model
\subsection{Effect of mixing}
\subsubsection{Continuous stirred tank approximation}
\subsubsection{Plug flow reactor approximation}

\subsection{Limiting regimes}
% plot error vs Pi 
\subsubsection{Mass transfer limited}
% sobol at low Pi -> Ks negligible
\subsubsection{Partial pressure limited}
% sobol at higher Pi -> Ks not negligible
\subsection{Analytical 0D model}
\subsubsection{Derivation}
Let us consider a single He bubble $b$, immersed in a static liquid of tritium concentration $c_l$. The evolution of the tritium inventory $n_{T_2,b}$ in the bubble is governed by:
\begin{equation}
\label{eq:nb}
    \frac{d\,n_{T_2,b}}{dt} = A_b\,\JT
\end{equation}

Writing it in terms of tritium partial pressure by using the ideal gas law and expanding the right term, \cref{eq:nb} becomes:

\begin{equation}
\label{eq:Pb_ODE}
    \frac{V_b}{RT}\frac{d\,\PT}{dt} = A_b\,h_l\,(c_l-K_s\PT)
\end{equation}

We are assuming a spherical bubble of diameter $d_b$, the specific interfacial area of the bubble is $a_b=\frac{A_b}{V_b}=\frac{6}{d_b}$ (not to be confused with the specific interfacial area of the gas phase as a whole $a=\varepsilon_ga_b$).
Solving \cref{eq:Pb_ODE} yields:
\begin{equation}
\label{eq:Pb_full}
    \PT(t)=\frac{c_l}{K_s}\,(1-e^{-a_b\,R\,T\,h_l\,K_s\,t})
\end{equation}

The speed $v_b$ of the bubble, assumed constant, couples the time it spends in the system to its position: $t=\frac{z}{v_b}$. We can express the member of the exponential term in \cref{eq:Pb_full} as a dimensionless number $\Pi$ defined as:
\begin{equation}
\label{eq:Pi_def}
    \Pi(z)\equiv \frac{a_b\,R\,T\,h_l\,K_s}{v_g}\,z
\end{equation}

$\Pi$ can be interpreted as "how close the bubble is to reaching $\frac{c_l}{K_s}$, i.e. being at equilibrium with the surrounding liquid". 
\begin{itemize}
    \item When $1-e^{\Pi(z)}\approx0$: the bubble can be considered free of any tritium, the driving force for tritium exchange \JT is therefore maximal, limited only by the liquid side mass transfer $h_l$, i.e. the ability of tritium to diffuse down the concentration gradient, through the liquid film up to the gas phase. 
    \item When $1-e^{\Pi(z)}\approx1$: the bubble is saturated with tritium, the interfacial flux \JT drops as there is no concentration gradient through the liquid film to drive it, since the mass transfer process is throttled by the partial pressure in the bubble being at equilibrium with the liquid phase.
\end{itemize}



(i.e. it can leave the boundary of the system eventually)
\subsubsection{Extension to partial pressure limited regime}
% fit e(Pi) with polynomial to get tau(Pi) 

%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Application to the LIBRA Pi tritium breeding experiment}
%%%%%%%%%%%%%%%%%%%%%%%%

\section{Prediction of the extraction time}

\subsection{Dependence on operating parameters}
\subsubsection{Sensitivity analysis}
% sobol plot of operating parameters
\subsubsection{Operating point}
% tau vs (n,T) map
% add cost function to give optimal region ?
\subsection{Uncertainty on transport parameters}
% given Pi number (previous chapter), can Ks be neglected
% pessimistic vs optimistic scenario

\section{Tritium permeation study}

\subsection{Tritium transport model}
\subsubsection{Geometry}
\subsubsection{Numerical scheme}
\subsection{Grid refinement study}

% safety factor SF=1.25 as recommanded for GCI on 3 or more grids
% we use P1 linear lagrange elements which theoretically give an L2 norm of the error in O(h^2) for the field themselves and O(h) for their gradient. Bounday fluxes are obtained from gradient so the results p=1-1.3 are consistent with the theory 

\subsection{Results}
\subsubsection{Impact of sweep gas composition}
\subsubsection{Impact of recombination constant}
\subsubsection{Effect of tritium extraction kinetics}


%%%%%%%%%%%%%%%%%%%%
\chapter{Evaluation}
%%%%%%%%%%%%%%%%%%%%

% In the evaluation you convince the reader that your design works as intended.
% Describe the evaluation setup, the designed experiments, and how the
% experiments showcase the individual points you want to prove.

% This section is usually 5-10 pages.


%%%%%%%%%%%%%%%%%%%%%%
\chapter{Related Work}
%%%%%%%%%%%%%%%%%%%%%%

The related work section covers closely related work. Here you can highlight
the related work, how it solved the problem, and why it solved a different
problem. Do not play down the importance of related work, all of these
systems have been published and evaluated! Say what is different and how
you overcome some of the weaknesses of related work by discussing the 
trade-offs. Stay positive!

This section is usually 3-5 pages.


%%%%%%%%%%%%%%%%%%%%
\chapter{Conclusion}
%%%%%%%%%%%%%%%%%%%%

In the conclusion you repeat the main result and finalize the discussion of
your project. Mention the core results and why as well as how your system
advances the status quo.

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
\printbibliography

% Appendices are optional
% \appendix
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \chapter{How to make a transmogrifier}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% In case you ever need an (optional) appendix.
%
% You need the following items:
% \begin{itemize}
% \item A box
% \item Crayons
% \item A self-aware 5-year old
% \end{itemize}

\end{document}